Projekt Medieninformatik\\Facial Expresson Recognition\\ Using A State Of The Art CNN

### 2018-01-10 doc/doc.tex
notes
chapters

\documentclass[a4paper,german]{report}

    \title{Projekt Medieninformatik}
    \date{WS17/18}
    \author{Lewe Ohlsen\\ Fachhochschule Wedel}

    \usepackage[utf8]{inputenc}                   % latin9 utf8
    \usepackage[german]{babel}
    \usepackage{tikz}
    \usepackage{pgfgantt}

    \begin{document}
        \maketitle
            \section{Section Headings}
            \begin{ganttchart}{1}{16}
                \gantttitle{Kalenderwoche}{16} \\
                \gantttitlelist{46,...,52,1,2,3,4,5,6,7,8,9}{1} \\

                \ganttbar{MNIST Tutorial}{1}{2} \\
                \ganttlinkedbar{Datenaufbereitung}{3}{3} \\
                \ganttbar{CNN-Inplementierung}{3}{9} \\

                %\ganttlinkedbar{Task 2}{3}{7} \ganttnewline
                \ganttmilestone{Webcam-Input}{7} \ganttnewline
                \ganttbar{Final Task}{8}{12}

@@

            \end{ganttchart}
    \end{document}

>>>>

\documentclass[a4paper,english]{report}

    \title{Projekt Medieninformatik\\Facial Expresson Recognition\\ Using A State Of The Art CNN}
    \date{WS17/18}
    \author{Lewe Ohlsen\\ Fachhochschule Wedel}

    \usepackage[utf8]{inputenc}  
    \usepackage[inline]{enumitem}
    \usepackage{tikz}
    \usepackage{pgfgantt}

    \begin{document}
        \maketitle
        \newpage
            \tableofcontents
        \newpage
        \section{Introduction}
            In order to get started with deep learning techniques and state of the art neural networks, I am participating in a Facial Expression Recognition Challenge\footnote{https://www.kaggle.com/c/challenges-in-representation-learning-facial-expression-recognition-challenge/data} on Kaggle. The goal is to build a classifier for facial expression recognition on live images.
        \section{Roadmap}
            \begin{ganttchart}{1}{16}
                \gantttitle{Calendar Week}{16} \\
                \gantttitlelist{46,...,52,1,2,3,4,5,6,7,8,9}{1} \\

                \ganttbar{MNIST Tutorial}{1}{2} \\
                \ganttlinkedbar{Data preparation}{3}{3} \\
                \ganttbar{implementing a simple linear model}{3}{4} \\                                
                \ganttlinkedbar{implementing a CNN}{4}{10} \\

                %\ganttlinkedbar{Task 2}{3}{7} \ganttnewline
                \ganttmilestone{processing Webcam images}{8} \ganttnewline
                \ganttlinkedbar{Tuning parameters}{10}{12}

@@

            \end{ganttchart}
        \chapter{About the Dataset}
        The Dataset consists of 48x48 pixel grayscale images of faces. The faces have been centered automatically do not require further preprocessing.
        The Dataset is initially being split into two subsets: The model is first trained to fit the training data and subsequently evaluated using the test dataset.

        % \begin{enumerate*}[label=(\roman*)]
        %     \item Training,\label{item:training}
        %     \item PublicTest and\label{item:pubtest}
        %     \item PrivateTest.\label{item:prvtest}
        % \end{enumerate*}\\
        % \ref{item:training} Dogs are very nice animals. However they need to be walked several times a day\ldots [continuous long passage spreading over multiple lines]\\
        % \ref{item:pubtest} Cats are often considered easier animals but\\
        % \ref{item:prvtest} Cats are often considered easier animals but\ldots

        \chapter{Feedforward Neural Networks}
        \section{Perceptrons}
        \section{Cost Function}
        \section{Optimizers}
        \section{Gradient Descend}
        \section{Backpropagation}        
        \chapter{Convolutional Neural Networks}
        \section{Convolutions}
        \section{Filters}
        \section{Layers and Dropouts}
        \chapter{Processing Live Images}
    \end{document}
